Physcraper: A Python package for continually updated gene trees

### 2020-06-23 physcraper_ms.Rmd
added bootstrap to methods

- The software MUSCLE [@edgar2004muscle] is implemented to perform alignments.
- First, all new sequences are aligned using default MUSCLE options.
- Then, a MUSCLE profile alignment is performed, in which the alignment of new sequences
  is aligned against the original alignment, working as a template. This ensures that
  the final alignment follows the homology criteria established by the original alignment.
- The final alignment is not further processed automatically. We encourage users
  to check it using any of the many tools for alignment processing, and eliminate
  columns with no information.

## Tree reconstruction

- A gene tree is reconstructed for each alignment provided, using RAxML [@stamatakis2014raxml] with 100 bootstrap replicates.
- The root of the tree is determined by finding the parent node of the sequences that do not belong to the ingroup. This ensures a correct rooting of the tree even when the search taxon is more inclusive than the ingroup.
- The final result is a tree for eac of the genes provided in the alignment.

## Tree comparison

- Gene trees are then coupled to conlict info.
- Conflict information can only be generated in the context of the whole Open Tree of
Life. Otherwise, it is not really possible to get conflict data.
***- One way to compare two independent phylogenetic trees is to compare them both to
the synthetic OToL and then measure how well they do against each other***

>>>>

- The software MUSCLE [@edgar2004muscle] is implemented to perform alignments.
- First, all new sequences are aligned using default MUSCLE options.
- Then, a MUSCLE profile alignment is performed, in which the original alignment
  is used as a template to align new sequences. This ensures that the final alignment
  follows the homology criteria established by the original alignment.
- The final alignment is not further processed automatically. We encourage users
  to check it using any of the many tools for alignment processing, and eliminate
  columns with no information.

## Tree reconstruction and comparison

- A gene tree is reconstructed for each alignment provided, using the software RAxML [@stamatakis2014raxml]
  with 100 classic bootstrap [@felsenstein1985confidence] replicates by default. The number of bootsrap replicates can be modified by the user.
  Other bootstrap types are transfer bootstrap expectation (TBE) recently proposed in @lemoine2018renewing.
- The final result is an updated phylogenetic hypothesis for each of the genes provided in the alignment.
- A conflict analysis is then run
- The root of the tree is determined by finding the parent node of the sequences that do not belong to the ingroup. This ensures a correct rooting of the tree even when the search taxon is more inclusive than the ingroup.
- Gene trees are then coupled to conlict info.
- Conflict information can only be generated in the context of the whole Open Tree of
Life. Otherwise, it is not really possible to get conflict data.
***- One way to compare two independent phylogenetic trees is to compare them both to
the synthetic OToL and then measure how well they do against each other***
